Manuscript 1 code

### 2024-10-03 manuscript_1_code.Rmd
corrected figure for 3b

cover_mod_fg <- glmmTMB(cover_trans ~ fg_richness_quad*habitat + (1|site/location) + (1|year), data = functional_richness_quad_cover)

summary(cover_mod_fg)
car::Anova(cover_mod_fg)
#                              Chisq Df Pr(>Chisq)    
# fg_richness_quad         10323.133  1  < 2.2e-16 ***
# habitat                     87.166  3  < 2.2e-16 ***
# fg_richness_quad:habitat    77.758  3  < 2.2e-16 ***
hist(residuals(cover_mod_fg)) # a little positive skew, not the worst

r.squaredGLMM(cover_mod_fg) # 0.39, 0.51
emtrends(cover_mod_fg, pairwise ~ habitat, var = "fg_richness_quad") 
#all habitats are different from forereef 17

>>>>

cover_mod_fg <- glmmTMB(cover_trans ~ fg_richness_quad*habitat + (1|site/location) + (1|year), family = beta_family(), data = functional_richness_quad_cover)

summary(cover_mod_fg)
car::Anova(cover_mod_fg)
#                              Chisq Df Pr(>Chisq)    
# fg_richness_quad         31341.052  1  < 2.2e-16 ***
# habitat                     49.887  3  8.444e-11 ***
# fg_richness_quad:habitat   447.780  3  < 2.2e-16 ***
hist(residuals(cover_mod_fg)) # good

r.squaredGLMM(cover_mod_fg) # 0.64, 0.65
emtrends(cover_mod_fg, pairwise ~ habitat, var = "fg_richness_quad") 
#all habitats are different from forereef 17
